\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}

%\usepackage{geometry}
\usepackage[inner=1.5cm,outer=1.5cm,top=2.5cm,bottom=2.5cm]{geometry}
\pagestyle{empty}
\usepackage{graphicx}
\usepackage{fancyhdr, lastpage, bbding, pmboxdraw}
\usepackage[usenames,dvipsnames]{color}
\usepackage{indentfirst}
\definecolor{darkblue}{rgb}{0,0,.6}
\definecolor{darkred}{rgb}{.7,0,0}
\definecolor{darkgreen}{rgb}{0,.6,0}
\definecolor{red}{rgb}{.98,0,0}
\usepackage[colorlinks,pagebackref,pdfusetitle,urlcolor=darkblue,citecolor=darkblue,linkcolor=darkred,bookmarksnumbered,plainpages=false,pdflang=en-US,pdftitle=AST4723_2024_SpectroscopyPlan]{hyperref}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\pagestyle{fancyplain}
\fancyhf{}
\lhead{ \fancyplain{}{AST4723} }
%\chead{ \fancyplain{}{} }
\rhead{ \fancyplain{}{\today} }
%\rfoot{\fancyplain{}{page \thepage\ of \pageref{LastPage}}}
\fancyfoot[RO, LE] {page \thepage\ of \pageref{LastPage} }
\thispagestyle{plain}

%%%%%%%%%%%% LISTING %%%
\usepackage{listings}
\usepackage{caption}
\DeclareCaptionFont{white}{\color{white}}
\DeclareCaptionFormat{listing}{\colorbox{gray}{\parbox{\textwidth}{#1#2#3}}}
\captionsetup[lstlisting]{format=listing,labelfont=white,textfont=white}
\usepackage{verbatim} % used to display code
\usepackage{fancyvrb}
\usepackage{acronym}
\usepackage{amsthm}
\VerbatimFootnotes % Required, otherwise verbatim does not work in footnotes!

\def\todo#1{\textcolor{red}{#1}}


\definecolor{OliveGreen}{cmyk}{0.64,0,0.95,0.40}
\definecolor{CadetBlue}{cmyk}{0.62,0.57,0.23,0}
\definecolor{lightlightgray}{gray}{0.93}



\lstset{
%language=bash,                          % Code langugage
basicstyle=\ttfamily,                   % Code font, Examples: \footnotesize, \ttfamily
keywordstyle=\color{OliveGreen},        % Keywords font ('*' = uppercase)
commentstyle=\color{gray},              % Comments font
numbers=left,                           % Line nums position
numberstyle=\tiny,                      % Line-numbers fonts
stepnumber=1,                           % Step between two line-numbers
numbersep=5pt,                          % How far are line-numbers from code
backgroundcolor=\color{lightlightgray}, % Choose background color
frame=none,                             % A frame around the code
tabsize=2,                              % Default tab size
captionpos=t,                           % Caption-position = bottom
breaklines=true,                        % Automatic line breaking?
breakatwhitespace=false,                % Automatic breaks only at whitespace?
showspaces=false,                       % Dont make spaces visible
showtabs=false,                         % Dont make tabls visible
columns=flexible,                       % Column format
morekeywords={__global__, __device__},  % CUDA specific keywords
}

\begin{document}

\title{Spectroscopy Observing Plan}
\maketitle


\section{Assignment}
Plan a spectroscopic observing run.  

 

You will observe:

\begin{itemize}
 \item A binary system with separation between 15" and 60" consisting of two medium-bright stars ($m_v < 10$)
 \item A bright ($m_v < 6$) A-star
 \item A bright ($m_v < 6$) M-star
 \item A spectrophotometric standard star with $m_v < 12$
 \item A bright nebula
 \item A dense star cluster
 \item A planet (and its moons if possible)
\end{itemize}
 

Your plan will include the following for each source:

\begin{itemize}
    \item {[5 pts]} Magnitude estimates in the blue, visual, and red
        filters.  (There are many different filter sets that include BVR
        filters, including Johnson, Cousins, Bessel, Strömgren.  Any are
        acceptable for this estimate.)
    \item {[10 pts]} Optical finder charts with a field of view of 15'.
        For the print version, use a white background with black stars.
         Finding an appropriate (unsaturated) finder chart can be quite tricky
         for our selection of bright sources; if the DSS doesn't have a good
         image, we will need to search for alternatives;
        \url{https://nova.astrometry.net/user_images/location}  may be a good option
        \emph{You need this finder chart accessible in both digital and print form:
        you will be using this document during your observing, so the quality of the 
        print will matter.}
    \item {[5 pts]} Contingency plans for observations in September, October, or
        November.  (Plan for September, but say what changes if you observe in
        late November instead).  Plan to observe from sunset to ~3.5 hours
        after sunset.
    \item {[5 pts]} A planned list of exposures and \emph{when} you will take them.
        These should be precise to the minute.  What CCD/CMOS images do you
        need?
\end{itemize}
 

 

\section{Reference Materials}
Spectrophotometric standard star lists

\begin{itemize}
    \item \url{https://www.eso.org/sci/observing/tools/standards/spectra.html}
    \item \url{https://www.eso.org/sci/observing/tools/standards/spectra/wdstandards.html}
    \item \url{http://mingus.mmto.arizona.edu/~bjw/mmt/spectro_standards.html}
    \item \url{https://www.naoj.org/Observing/Instruments/FOCAS/Detail/UsersGuide/Observing/StandardStar/Spec/SpecStandard.html}
    \item \url{https://noirlab.edu/science/observing-noirlab/observing-ctio/Spectrophotometric-Standards}
\end{itemize}
 

Binary star lists:

\begin{itemize}
    \item \url{https://www.astroleague.org/files/u220/DS-MasterObjectList2021.pdf}
    \item \url{http://www.ianridpath.com/binaries.html}
\end{itemize}

\section{Turn In:}
\begin{itemize}
    \item Your observing plan
    \item Your complete work notebook in .ipynb (if you used jupyter) and .pdf form 
\end{itemize}


\end{document}
% resource: https://www.youtube.com/watch?v=_eMNRa-KEiQ
